### 2023-04-04 chapter2/chapter2.tex
Added text for IDR prediction and filtering method

\subsection{IDR prediction and filtering}

>>>>

\subsection{IDR prediction and filtering}
AUCPreD was used to predict the disorder score of each residue of each sequence in the alignments after the gap symbols were removed~\cite{Wang2016}. The resulting scores were then aligned using the original alignment. The average score for each position was calculated using Gaussian process sequencing weighting over the LG consensus tree~\cite{Altschul1989}. Any positions inferred as ``missing'' by the missing data phylo-HMM or to the left or right of the first or last non-gap symbol, respectively, were excluded. For simplicity, the Gaussian process weights were not re-calculated from a tree pruned of the corresponding tips, and instead the weights corresponding to the remaining sequences were re-normalized. The scores at any remaining positions with gap symbols were inferred by linear interpolation from the nearest scored position.

The average disorder scores were converted into contiguous regions with the following method. First, two binary masks were defined as positions where the average score exceeded high and low cutoffs of 0.6 and 0.4, respectively. The low-cutoff mask was subjected to an additional binary dilation operation with a structuring element of size three to merge any contiguous regions separated by a small number of positions with scores below the cutoff. ``Seed'' regions were then defined as 10 or more contiguous ``true'' positions in the high-cutoff mask, and ``disorder'' regions were obtained by expanding the seeds to the left and right until the first ``false'' position in the low-cutoff mask or the end of the alignment. ``Order'' regions were defined as the complement of the disorder regions in each alignment.

The regions were filtered with the following criteria. First, segments with non-standard amino acid symbols, which overlapped with any position labeled as ``missing'' by the missing data phylo-HMM, or whose number of non-gap symbols was below a length cutoff were removed. Regions whose remaining segments satisfied the set of phylogenetic diversity criteria detailed in Table~\ref{stable:diversity_criteria} were included in the final set. The length cutoffs were set to 30, 60, and 90 residues, which generated three distinct sets of regions.
